Eco-evolutionary dynamics of finite populations from first principles

### 2023-04-24 MS_thesis.tex
Rephrase acknowledgements

I would also like to thank Prof. Sutirth Dey, my expert for this project. Sutirth provided constructive comments during the mid-year evaluation that helped me re-evaluate my project and its goals. Sutirth's brilliant course on evolution at IISER and various fascinating conversations with him and other lab members during my time as an intern at the \href{https://sites.google.com/a/acads.iiserpune.ac.in/sdlab/pbl-iiser-p}{Population Biology Lab} have been instrumental in shaping my thoughts on evolution. I am also extremely grateful to Dr. Anand Krishnan for constantly supporting me and always being there, both as a mentor and a friend, when I needed advice --- Thank you for everything.

>>>>

Prof. Sutirth Dey provided constructive comments during evaluation that greatly improved this thesis. Sutirth's brilliant course on evolution at IISER and various fascinating conversations with him and other lab members during my time at the \href{https://sites.google.com/a/acads.iiserpune.ac.in/sdlab/pbl-iiser-p}{Population Biology Lab} have been instrumental in shaping my thoughts on evolution. I would like to thank Prof. Deepak Dhar for reviewing this thesis and providing insightful comments that greatly improved its content. I am also extremely grateful to Dr. Anand Krishnan for constantly supporting me and always being there, both as a mentor and a friend, when I needed advice.
